Factoring with $n+2$ clean qubits and $n-1$ dirty qubits

### 2017-06-13 doc/paper.tex
Thinko fix
Polishing paper content - Added note about constant factors being important - Rewrote some of the conclusion - Added QFT inverting multiplication remarks to conclusion - Fixed dependency diagram saying "scale-accumulate" instead of "scale-add".

@@

Because our modular circuit constructions would have undefined behavior if any register had a value equal to or larger than $R$, we need the ancilla register to contain a value less than $R$.
We ensure this by requiring that the ancilla register's MSB be $|0\rangle$ (i.e. clean) and that the registers be as small as possible (i.e. have size $n = \lceil \lg_2(R-1) \rceil$, because only values up to $R-1$ need to be stored).

@@

Of the $2n+1$ qubits our period-finding construction requires: $1$ is used for the phase estimation qubit, $n$ are used to store the work register, and $n$ are ancillae used to implement modular multiplication in terms of scaled modular addition.
Except for multiplication, all our arithmetic constructions use two or fewer dirty ancillae.
Since we reduce modular scale-addition into operations that have a $\Theta(n)$ surplus of unused qubits, in context there are always more than enough dirty ancillae available to implement the simpler arithmetic inline.
Because there is slack in the simpler arithmetic constructions, improving the overall number of qubits used by Shor's algorithm requires only that we improve the first step of reducing modular multiplication into some other operation.

@@

The number of clean qubits required to perform Shor's algorithm is now $n + O(1)$.
We consider this improvement to be a step towards a construction for Shor's algorithm that uses only $n + O(1)$ qubits total.
Such a construction could, by allowing factoring problems to fit into quantum computers with half as much space, reduce the time until it's possible to break current cryptographic keys by months or years (depending on how quickly quantum computers gain capacity, the constant factors of the construction, and the trade-offs between space, error correction, and qubit coherence time).

>>>>

Our circuit constructions are not optimized to achieve good constant factors on circuit depth or gate count.
Our constructions also ignore machine architecture; they assume all-to-all connectivity between qubits.
Achieving small constant factors under realistic architectural constraints is an important practical problem, but not the focus of this paper.

@@

Because our modular circuit constructions would have undefined behavior if any register had a value equal to or larger than $R$, we need the ancilla register to contain a value less than $R$.
We ensure this by requiring that the ancilla register's MSB be $|0\rangle$ (i.e. clean) and that the registers be as small as possible (i.e. have size $n = \lceil \lg_2(R) \rceil$).

@@

Of the $2n+1$ qubits our period-finding construction requires, $1$ is used for the phase estimation qubit, $n$ are used to store the work register, and $n$ are ancillae used to implement modular multiplication in terms of scaled modular addition.
Except for multiplication, all our arithmetic constructions use two or fewer dirty ancillae.
Since we reduce modular scale-addition into operations that have a $\Theta(n)$ surplus of unused qubits, in context there are always more than enough dirty ancillae available to implement the simpler arithmetic inline.
Because there is slack in the simpler arithmetic constructions, improving the overall number of qubits used by Shor's algorithm requires only that we improve the first step of reducing modular multiplication into some other operation.

@@

A second way to reduce modular multiplication into (slightly) smaller operations could be with commutator control.
Note that the modular Fourier transform inverts the effect of modular multiplication: $QFT_{R} \cdot (\times K) \cdot QFT_R^{-1} = (\times K^{-1}) \pmod{R}$.
This has two useful high-level effects.
First, by applying the bimultiplication gate used in this paper twice, but inverting the effect on the ancilla register for the second application, we can build a proper modular multiplication gate that only affects a single register.
Second, we can use commutator control to move controls from the modular multiplication gate onto modular Fourier transform gates.
Assuming controlled modular QFTs can be performed with fewer ancillae than controlled modular multiplication, we could save a dirty ancilla when performing the modular multiplication by borrowing the control qubit.

Possible future improvements aside, in this paper we showed that a number of clean qubits sufficient to perform Shor's algorithm is $n + O(1)$.
We consider this improvement to be a step towards a construction for Shor's algorithm that uses only $n + O(1)$ qubits total.
Such a construction could, by allowing factoring problems to fit into quantum computers with half as much space, reduce the time until it's possible to break current cryptographic keys by months or years (depending on how quickly quantum computers gain capacity, the constant factors of the construction, and the trade-offs between space, error correction, and qubit coherence time).
